MNRAS \LaTeXe\ template -- title goes here

### 2018-08-23 paper.tex
removing files
Adding some subsection titles and bullet points (mostly previous work)

@@

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\section{Methods/Cosmological Simulations}

@@

@@

@@

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
Others S., 2012, Journal of Interesting Stuff, 17, 198
\end{thebibliography}

>>>>

\input{macros.tex}

@@

% These dates will be filled out by the publisher
%\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\li Here are some relevant papers that studied the minimum halo mass
with simulations or ones that developed an analytical model of the
halo mass.  We will probably cite most of these in the introduction.

\lli Semi-analytic papers: \citep{Tegmark97, Trenti09, Visbal18,
  Mebane18, Griffen18}

\lli Simulation papers: \citep{Machacek01, Yoshida03, Wise07_UVB,
  OShea08, Muratov13}

\lli {\it Note:} I looked at which papers cited the \citet{Machacek01}
paper to look for recent papers.  I didn't find any in the past five
years that used simulations to study the minimum halo mass.

\section{Methods}

\subsection{Simulation setup}

We used Enzo \citep{Enzo}.

\subsection{Star formation and feedback}

@@

\subsection{Population III host halo masses}

\subsection{Multiple stellar systems}

\subsection{Population III stars in atomic cooling halos}

@@

\subsection{Variations in the halo masses at collapse}

\li Halos can form metal-free stars again if their progenitors had
only formed stars that did not go supernova

\li Dynamical heating \citep{Yoshida03}

\li Temporal fluctuations in the local Lyman-Werner radiation

\subsection{Comparison to previous work}

\li Semi-analytic papers: \citep{Tegmark97, Trenti09, Visbal18,
  Mebane18, Griffen18}

\li Simulation papers: \citep{Machacek01, Yoshida03, Wise07_UVB,
  OShea08, Muratov13}

\li We don't have to compare with all of the semi-analytic papers, but
it will be good to compare with all of the simulation papers.

\subsection{Caveats}

\li Optically-thin Lyman-Werner radiation field from point sources \citep{Schauer17}

\li No streaming velocities that suppresses star formation at very
high ($z \ga 20$) redshifts \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}

\li Uncertainties from the assumed Pop III initial mass function

@@

\bibliographystyle{mnras}
\bibliography{jwise} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\end{thebibliography}
